Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2020-02-14 Tex/Old text/chapters/chapteroptimization.tex
thesis update

All experiments regarding the verification tools were conducted 
on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
$2.90$ GHz and $64$ GB RAM, running Ubuntu $16.04$ LTS $64$-bits. 
For HOMER Pro, an Intel Core i5-$4210$ ($4$-cores) was used, 
with $1.7$ GHz and $4$ GB RAM, running Windows 10. 
The experiments were conducted with a predefined time-out of $240$ minutes.

Three start-of-the-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc -benchmark filename.c} version 1.8 in a configuration as bound model checking and with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency. An ``incremental'' ESBMC with the SMT solver Z3 version 4.7.1~\cite{DeMoura} was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.

@@

\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P+2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & TO & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{SAT (605 min) \\NTP:6$\times$330W (2P+3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S+2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70}  & \makecell {SAT (254.25 min) \\NTP:4$\times$330W (2S+2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & UNSAT (0.48 min) & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = time out; IF = internal failure, E = energy.
\end{scriptsize}
\end{table}

CPAchecker was able to synthesize optimal sizing in six 
out of the seven case studies (cases $1$ - $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes. Fig.~\ref{fig:CPAoptc1} illustrates the result of case 4 with the optimal sizing appearing on the left size as the integer $8$ for the solar panel (which is the model RSM36-6-150P from the manufacturer Risen), battery $0$ refers to the model 12MF80 of 80 Ah from Moura, charge controller $1$ refers to the model 15A-75V MPPT from Victron  Energy, and the inverter number $3$ refers to the model IP350-11 from Epever (750 W). The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, also presented in the counterexample as well, shows the number of panels and batteries and how they are connected.

Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e.  it was not solved within $240$ minutes. This is illustrated in Fig.~\ref{fig:cpaoptcase7}. However, this CPAchecker time-out limitation is removed, the verifier is able to solve the optimization in $44.97$ hours.

The violation (SAT result) indicated all over the Table~\ref{tab1} 
is the $assert$ of line $21$ from Algorithm~\ref{alg:verification-algorithm}. %The results were tested by manual PV sizing and were sound (\textit{RQ1}). %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code.

\begin{figure}[h]
\includegraphics[width=1.0\textwidth]{CPA_opt_c4.png}
\centering
\caption{Counterexample generated by CPAchecker after validation of case 4 (file Counterexample.html).}
\label{fig:CPAoptc1}
\end{figure}

\begin{figure}[h]
\includegraphics[width=1.0\textwidth]{CPAchecker_timeout_case7.png}
\centering
\caption{CPAchecker time out result for case 7 optimization (file CPALog.txt).}
\label{fig:cpaoptcase7}
\end{figure}

An internal failure was presented by ESBMC when using Z3 solver in all case studies. It corresponds to a 'bug' at the Z3 solver which will require an updated version of ESBMC to fix it. CBMC was unable to produce any conclusive result. \textit{Out of memory} situations occurred in all case studies. Those specific results partially answers the \textit{EQ2}

ESBMC are unable to produce any conclusive result. \textit{Internal failure}, \textit{time out}, or \textit{out of memory} situations occurred; this partially answers the \textit{EQ2}.  Similar to CPAchecker, if the \textit{time out} is removed from ESBMC with the SMT solver Boolector, then the verifier is able to obtain the automated synthesis in $73.18$ hours for case study $2$.

@@

Comparing the results of the formal synthesis against those of CPAchecker and HOMER Pro, it was observed that most results are quite similar, 
in terms of technical solution and cost (cf. Table~\ref{tab1}).

Particularly in the case of LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with differences varying from $0.23$\% to $17.4$\%. Even adopting the same price per kW for PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into the CPAchecker modeling. The premise used in CPAchecker to adopt a fixed annual cost for operation and maintenance can produce some impact as well on this discrepancy; however, it is not significant since the annual cost is too small when compared to the resulting LCC value.

However, there exists a huge divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than the automated synthesis tool, probably because the operation and maintenance costs assumed by the automated synthesis tool were underestimated for that specific load.

In general, the PV panels and battery bank were larger in HOMER Pro than with the formal synthesis approach, and that discrepancy is not easy to address without some real systems validation. The mathematical models are different and particular parameters can be tuned as well in each approach, and that can justify the difference, which was presented in all the case studies. As a comparison, consider case study $1$: the optimal solution provided by HOMER Pro requires $7$ $times$ more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e. the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $500.4$ Ah ($6 \times 83.4$), while the synthesis tool presented an optimal solution with a total capacity of $420$ Ah ($4 \times 105$).

Comparing the optimization results with those the real-world, the author had four PV systems deployed and monitored since June $2018$ in a riverside community in State pf Amazonas, Brazil, with demands  similar to those of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries. These solutions are closer to the result presented by the proposed formal synthesis approach than that of HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.

@@

Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase. Case study $3$ could not be simulated in HOMER Pro, because of its restriction on setting battery autonomy, thus leaving both without parameters to compare.

@@

Comparison of verifiers with the proposed automated synthesis using model checking was made, in order to obtain the optimal sizing of stand-alone solar PV systems, which showed that CPAchecker had the best overall performance. CBMC and ESBMC were not conclusive for all the cases, reaching the \textit{time out} stipulated ($240$ minutes) or being \textit{out of memory}. CPAchecker was unable to present a conclusive result only in case $7$ (\textit{time out}).

A comparison with a specialized simulation tool was also made, however only $5$ case studies (case $1$, case $2$, case $4$, case $5$, and case $6$) compared to the presented result. Some limitations of the simulation tool, mainly related to not allowing battery autonomy setup, and the $time-out$ or $out of memory$ messages presented by the verifiers, restricted the comparison between the automated verification tools and the simulation tools. However, when the comparison was possible, it was noticeable that the LCC came very close, and that HOMER Pro overestimated the sizing.

>>>>

All experiments regarding the verification tools were conducted 
on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with 
$2.90$ GHz and $64$ GB RAM, running Ubuntu $16.04$ LTS $64$-bits. 
For HOMER Pro, an Intel Core i5-$4210$ ($4$-cores) was used, 
with $1.7$ GHz and $4$ GB RAM, running Windows 10. 
The experiments were conducted with a predefined time-out of $660$ minutes.

Three start-of-the-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-incremental-bmc -\phantom{}-boolector} version 6.0.0 configured for incremental loop unwinding verification with the  Boolector 3.0.1 solver~\cite{Brummayer},  %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, ESBMC {Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc -benchmark filename.c} version 1.8 in a configuration as bound model checking and with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency. An ``incremental'' ESBMC with the SMT solver Z3 version 4.7.1~\cite{DeMoura} was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory.

@@

\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P-2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & TO & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{SAT (605 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70}  & \makecell {SAT (254.25 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & UNSAT (0.48 min) & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = time out; IF = internal failure, E = energy.
\end{scriptsize}
\end{table}

The violation (SAT result) indicated all over the Table~\ref{tab1} 
is the $assert$ of line $21$ from Algorithm~\ref{alg:verification-algorithm} and indicates that an optimal solution was found.

CBMC was unable to produce any conclusive result. \textit{Out of memory} situations occurred in all case studies.

CPAchecker was able to synthesize optimal sizing in three out of the seven case studies (cases $1$, $4$, and $5$): the result was produced within the time limit, which varied from $254.25$ to $548$ minutes. Fig.~\ref{fig:CPAoptc1} illustrates the result of case $5$ with the optimal sizing appearing on the left size as the integer $3$ for the solar panel (which is the Canadian CS6U-330P model of $330$ W from the manufacturer Victron Energy), battery $0$ refers to the model 12MF80 of $80$ Ah from Moura, charge controller $0$ refers to the model 35A-145V MPPT from Victron  Energy, and the inverter number $2$ refers to the Epever model IP350-11 of $280$ W (nominal power) and $750$ W of surge power. The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, also presented in the counterexample as well, shows the number of panels and batteries and how they are connected.

Case studies $2$, $3$, $6$, and $7$  led to a \textit{time out} result in CPAchecker, i.e.  it was not solved within $660$ minutes.

\begin{figure}[h]
\fbox{\includegraphics[width=1.0\textwidth]{CPA_opt_c5.png}}
\centering
\caption{Counterexample generated by CPAchecker after validation of case 5 (file Counterexample.html).}
\label{fig:CPAoptc1}
\end{figure}

An internal failure was presented by ESBMC when using Z3 solver in all case studies. It corresponds to a 'bug' in the Z3 solver which will require an updated version of ESBMC to fix it. However, when using the incremental BMC configuration of ESBMC with Boolector solver, the verifier engine was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response varying from $36.70$ to $620$ minutes. Fig.~\ref{fig:esbmcoptcase3} shows the counterexample generated.  ESBMC with this configuration was not possible to obtain a optimal solution in cases $2$ and $7$. Case $2$ reached a  \textit{time out} result after $660$ minutes of processing. Moreover, case $7$ resulted in a UNSAT result, i.e the verifier engine was not possible to get a feasible solution considering the list of equipment. This SAT situation was reached after just $0.48$ minutes.

\begin{figure}[h]
\fbox{\includegraphics[width=1.0\textwidth]{ESBMC_SAT_case3.png}}
\centering
\caption{ESBMC counterexample for case 3 optimization.}
\label{fig:esbmcoptcase3}
\end{figure}

Those specific results partially answers the \textit{EQ2}.

@@

Comparing the results of the formal synthesis with CPAchecker, and ESBMC, against those of  HOMER Pro, it was observed some distinct results, in terms of technical solution and cost (cf. Table~\ref{tab1}).  Related to performance there is a huge difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in opposite of an average of $234$ minutes for the automated synthesis technique.

Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, always having a higher estimation from the automated synthesis technique. However, considering that the cost of individual item of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.

In one hand, related to the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the produced by the simulation tool. The difference varied from $19$\% to $65$\%. In the other hand, related to the battery bank, the results were smaller in terms of capacity to the HOMER Pro. The difference was among $34$\% to $68$\%.

Those discrepancies are not easy to address without some real systems validation. The mathematical models are different and particular parameters can be tuned as well in each technique, and that can justify the difference, which was presented in all the case studies.

As a comparison, consider case study $5$: the optimal solution provided by HOMER Pro requires $17$\% more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e. the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $417$ Ah ($5 \times 83.4$ Ah), while the synthesis tool presented an optimal solution with a total capacity of $560$ Ah ($7 \times 80$ Ah) and this represent a difference of $34$\%.

Comparing the optimization results with those the real-world, the author had four PV systems deployed and monitored since June $2018$ in a riverside community in State pf Amazonas, Brazil, with demands  similar to those of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries. These solutions are closer to the results from PV panel, controller and inverter presented by the proposed formal synthesis approach than that of HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}. However the solution presented for the battery bank is very different.

@@

Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase. Case study $2$ was solved just by the ESBMC verifier engine. Case study $3$ could not be simulated in HOMER Pro, because of its restriction on setting battery autonomy, thus leaving those three cases without parameters to compare.

@@

Comparison of verifiers with the proposed automated synthesis using model checking was made, in order to obtain the optimal sizing of stand-alone solar PV systems, which showed that ESBMC had the best overall performance. CBMC was not conclusive for all the cases, and CPAchecker was unable to present a conclusive result in cases $2$, $3$, and $7$,  (\textit{time out}).

A comparison with a specialized simulation tool was also made, however only $4$ case studies (case $1$, case $4$, case $5$, and case $6$) compared to the presented result. Some limitations of the simulation tool, mainly related to not allowing battery autonomy setup, and the $time-out$ or $out \, of \, memory$ messages presented by the verifiers, restricted the comparison between the automated verification tools and the simulation tools. However, when the comparison was possible, it was noticeable that the LCC was not so distant, that HOMER Pro produces a bigger PV panel sizing, and moreover that the synthesis tool produces bigger battery bank.

### 2020-02-14 Tex/Old text/chapters/conclusion.tex
thesis update

The first contribution was presented in ~\autoref{chap:automatedverification}, we described and evaluated an automated verification method of validating a given stand-alone PV system. Our method, using model checking, can perform a size check and verify, over time, whether a PV system meets electrical requirements. There are various possible ways to perform that validation, such as testing, laboratory measuring, or even simulation. However, we developed an algorithm and a tool using model checking that is feasible and effective. Our results were supported by case studies, by data gathered from the field, and by interviews with PV owners.

We analyzed five case studies of real PV systems deployed in five different sites, ranging from $975$ W to $1,300$ W (inverter specification), and the results of three state-of-the-art verification engines (ESBMC, CBMC, and CPAchecker). Although the verification method that we proposed takes longer than the simulation methods, it can avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$. We validate these results by the sized systems deployed in the field.

@@

%In a nutshell, our proposed PV system validation method, who check the size of inputted PV system, and verifies it over the time, was feasible and effective, supported by a algorithm written to implement the method, by a comparative with a commercial simulation tool, and by real data collect at the field.
%
In the comparison among verification engines, ESBMC with the SMT solver Z3 executed in the ``incremental SMT'' configuration presented a better performance than CBMC (around four times faster), used less RAM than CBMC and CPAchecker (less than $2$ GB when compared to $9.2$ GB for CBMC and 19.2GB for CPAchecker) as expected and explained in Section~\ref{sec:ESBMC}. All our experimental results are sound since the PV owners and the monitoring system validated the possible flaws that the system could present in the field.
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.

@@

We proposed a variant of the CEGIS synthesis process, working with just one feasible solution from the {\sc Synthesize} phase and refinement from the iterative search from the {\sc Verify} phase. Using this approach, we obtain the optimization of stand-alone PV systems, arriving at the best compromise between power reliability and system cost analysis. Our algorithm that implements this method uses a database of commercially available equipment, including the price. Furthermore, in order to validate our method, we conducted seven case studies of PV systems on two different sites in the State of Amazonas, Brazil, ranging from $253$\,W to a $1,586$\,W peak; and three state-of-the-art verification engines were considered (ESBMC, CBMC, and CPAchecker). In addition, we again used the specialized off-the-shelf simulation tool (HOMER Pro) to compare the results. In terms of performance and best results, CPAchecker was the most successful and used for the comparison with the simulation tool.

In summary, our synthesis proposal is capable of presenting a solution which is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro. In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the component model, nominal current, and voltage. We also cover the charge controller, which is unavailable in HOMER Pro. Note that our automated synthesis tool took longer to find the optimal solution than HOMER Pro. However, the solution presented is sound and complete; it also provides a list of equipment that can be bought direct from the manufacturer.

>>>>

The first contribution was presented in~\autoref{chap:automatedverification}, we described and evaluated an automated verification method of validating a given stand-alone PV system. Our method, using model checking, can perform a size check and verify, over time, whether a PV system meets electrical requirements. There are various possible ways to perform that validation, such as testing, laboratory measuring, or even simulation. However, we developed an algorithm and a tool using model checking that is feasible and effective, although our technique does not replace the others. Our results were supported by case studies, by data gathered from the field, and by interviews with PV owners.

We analyzed five case studies of real PV systems deployed in five different sites, ranging from $975$ W to $1,300$ W (inverter specification), and the results of three state-of-the-art verification engines (ESBMC, CBMC, and CPAchecker).The verification method with ESBMC was faster than the simulation method. We validate the overall results by the sized systems deployed in the field.

@@

%In a nutshell, our proposed PV system validation method, who check the size of inputted PV system, and verifies it over the time, was feasible and effective, supported by a algorithm written to implement the method, by a comparative with a commercial simulation tool, and by real data collect at the field.
%
In the comparison among verification engines, ESBMC with the SMT solver Z3 executed in the ``incremental SMT'' configuration presented a better performance than CBMC, used less RAM than CBMC and CPAchecker as expected and explained in Section~\ref{sec:ESBMC}. All our experimental results are sound since the PV owners and the monitoring system validated the possible flaws that the system could present in the field.
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.

@@

We proposed a variant of the CEGIS synthesis process, working with just one feasible solution from the {\sc Synthesize} phase and refinement from the iterative search from the {\sc Verify} phase. Using this approach, we obtain the optimization of stand-alone PV systems, arriving at the best compromise between power reliability and system cost analysis. Our algorithm that implements this method uses a database of commercially available equipment, including the price. Furthermore, in order to validate our method, we conducted seven case studies of PV systems on two different sites in the State of Amazonas, Brazil, ranging from $253$\,W to a $1,586$\,W peak; and three state-of-the-art verification engines were considered (ESBMC, CBMC, and CPAchecker). In addition, we again used the specialized off-the-shelf simulation tool (HOMER Pro) to compare the results. In terms of performance and best results, ESBMC was the most successful and used for the comparison with the simulation tool.

In summary, our synthesis proposal is capable of presenting a solution which is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro. In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer data sheet, including the component model, nominal current, and voltage. We also cover the charge controller, which is unavailable in HOMER Pro. Note that our automated synthesis tool took longer to find the optimal solution than HOMER Pro. However, the solution presented is sound and complete; it also provides a list of equipment that can be bought direct from the manufacturer.

### 2020-02-14 Tex/Old text/chapters/introduction.tex
thesis update

\textcolor{red}{Optimization is important when there exist (just) the requirements of the house to be electrified. In our particular case, we need a optimal PV system solution, in technical and economical terms, that can show us a list of equipment to be bought and how it will be connected together (configuration)}.

@@

\textcolor{red}{My comment: paragraphs broken in small and organized parts:}

>>>>

Optimization is important when there exist (just) the requirements of the house to be electrified. In our particular case, we need a optimal PV system solution, in technical and economical terms, that can show us a list of equipment to be bought and how it will be connected together (configuration).

@@
